Dynamic Modeling, Parameter Estimation and Uncertainty Analysis in \proglang{R}

### 2017-09-19 article.tex
Modify format of table

%% The address of (at least) one author should be given
%% in the following format:
\Address{
  Daniel Kaschek\\
  Institute of Physics, University of Freiburg\\
  Hermann-Herder-Str.~3\\
  79104 Freiburg, Germany\\
  E-mail: \email{daniel.kaschek@physik.uni-freiburg.de}
  %URL: \url{http://eeecon.uibk.ac.at/~zeileis/}
}
%% It is also possible to add a telephone and fax number
%% before the e-mail in the following format:
%% Telephone: +43/512/507-7103
%% Fax: +43/512/507-2851

@@

\begin{table}[ht]
	\caption{Overview of the \pkg{dMod} core functionality and comparison with other packages.}
	\label{tab:comparison}
	\begin{tabular}{m{7cm}||c|c|c|c|c}
		& dMod & FME & nlmeODE & scaRabee & mkin\\
		\hline
		\hline
		facilitated set-up of ODE models with automated \proglang{C} code generation for fast simulation of model predictions and model sensitivities & $+$ & $(+)^1$ & $-$ & $-$ & $(+)^1$ \\
		\hline
		flexible set-up of general parameter transformations (explicit or implicit) and observation functions, allowing for the implementation of multiple experimental conditions similar to mixed-effects modeling & $+$ & $-$ & $(+)^2$ & $(+)^2$ & $-$ \\
		\hline
		parameter estimation based on trust-region optimization of the negative log-likelihood, making use of the sensitivity equations of the dynamic system and of symbolic derivatives of the observation- and parameter transformation functions & $+$ & $-$ & $-$ & $-$ & $-$ \\
		\hline
		identifiability and uncertainty analysis based on the profile-likelihood method to determine confidence intervals for parameters and predictions & $+$ & $(-)^3$ & $-$ & $-$ & $-$ \\
		\hline
	\end{tabular}
	\vspace{0.1em}

	\begin{footnotesize}
		$^1$Only ODE, no sensitivity equations generated. $^2$Mixed-effects modeling allows to define parameters in a condition-specific manner. $^3$Other methods used, e.g.~the collinearity method \citep{brun2001practical}. 
	\end{footnotesize}
\end{table}

>>>>

%% The address of (at least) one author should be given
%% in the following format:
\Address{
  Daniel Kaschek\\
  Institute of Physics, University of Freiburg\\
  Hermann-Herder-Str.~3\\
  79104 Freiburg, Germany\\
  E-mail: \email{daniel.kaschek@gmail.com}
  %URL: \url{http://eeecon.uibk.ac.at/~zeileis/}
}
%% It is also possible to add a telephone and fax number
%% before the e-mail in the following format:
%% Telephone: +43/512/507-7103
%% Fax: +43/512/507-2851

@@

\begin{table}[ht]
	\caption{Overview of the \pkg{dMod} core functionality and comparison with other packages.}
	\label{tab:comparison}
	\begin{scriptsize}
		\begin{center}
			\begin{tabular}{m{7cm}||c|c|c|c|c}
				& dMod & FME & nlmeODE & scaRabee & mkin\\
				\hline
				\hline
				facilitated set-up of ODE models with automated \proglang{C} code generation for fast simulation of model predictions and model sensitivities & $+$ & $(+)^1$ & $-$ & $-$ & $(+)^1$ \\
				\hline
				flexible set-up of general parameter transformations (explicit or implicit) and observation functions, allowing for the implementation of multiple experimental conditions similar to mixed-effects modeling & $+$ & $-$ & $(+)^2$ & $(+)^2$ & $-$ \\
				\hline
				parameter estimation based on trust-region optimization of the negative log-likelihood, making use of the sensitivity equations of the dynamic system and of symbolic derivatives of the observation- and parameter transformation functions & $+$ & $-$ & $-$ & $-$ & $-$ \\
				\hline
				identifiability and uncertainty analysis based on the profile-likelihood method to determine confidence intervals for parameters and predictions & $+$ & $(-)^3$ & $-$ & $-$ & $-$ \\
				\hline
			\end{tabular}
		\end{center}
	\end{scriptsize}
	\vspace{0.1em}

	\begin{scriptsize}
		$^1$Only ODE, no sensitivity equations generated. $^2$Mixed-effects modeling allows to define parameters in a condition-specific manner. $^3$Other methods used, e.g.~the collinearity method \citep{brun2001practical}. 
	\end{scriptsize}
\end{table}
